Attribute fusion in a latent process model for time series of graphs

### 2011-05-12 ssp2011.tex
Written proof of limsup scan \leq lim max degree

  Let $\phi_{\lambda}(v;t^{*}) = \psi_{\lambda}(v;t^{*}) -
  d_{\lambda}(v;t^{*})$. Let $d_{\zeta}(v;t)$ be
the number of neighbors of $v$ that lies in $[m]$ and
$d_{\xi}(v;t)$ be the number of neighbors of $v$ that lies in $[n]
\setminus [m]$. The following statements are made, conditional on $d_{\zeta}(v;t^{*}) =
l_{\zeta}$ and $d_{\xi}(v;t^{*}) = l_{\xi}$. First of all, we have

@@

  \phi_{\lambda}(v;t^{*}) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +

@@

@@

  \frac{\phi_{\lambda}(v;t^{*}) - \rho}{\varsigma} \rightsquigarrow

@@

l_{\xi}, p_{10} \Bigr)$. By the central limit theorem, we have

@@

 \frac{\phi_{\lambda}(v;t^{*}) - \rho}{\varsigma} \rightsquigarrow
 \frac{Y_{\zeta} + Y_{\xi} + Y_{\omega} - \rho}{\varsigma}

@@

Eq.~\eqref{eq:21} states that the locality statistics for our
attributed random graphs model time $t = t^{*}$ can be approximated by
the locality statistics for an unattributed kidney and egg model. We
thus define $Y(v) = Y_{\zeta}(v) + Y_{\xi}(v) + Y_{\omega}(v)$
where $Y_{\zeta}(v) \sim C_{11}
\mathrm{Bin}(\tbinom{d_{\zeta}(v;t)}{2}, p_{11})$ and $Y_{\xi},
Y_{\omega}$ are defined accordingly. Let $G \sim \kappa(n,m,p_{11},
p_{10}, p_{00})$ be an unattributed kidney-egg graph with the

@@

being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. Let $M(v)$ and
$W(v)$ denote the number of vertices adjacent to $v$ in $[m]$ and $[n]
\setminus [m]$, respectively. $D(v) = M(v) + W(v)$ is then the degree

@@

    &= P_1 + P_2

@@

\end{proof}
\end{proof}
\bibliography{ssp2011}
\end{document}

>>>>

  For ease of exposition, we will drop the time index $t =
  t^{*}$ from our notations and discussion. Let
  $\phi_{\lambda}(v) = \psi_{\lambda}(v) - d_{\lambda}(v)$. Let
  $M(v)$ be the number of neighbors of $v$ that lies in $[m]$ and
  $W(v)$ be the number of neighbors of $v$ that lies in $[n]
\setminus [m]$. The following statements are made, conditional on
$M(v) = l_{\zeta}$ and $W(v) = l_{\xi}$. We have

@@

  \phi_{\lambda}(v) = \sum_{k=1}^{K} \lambda_k ( y^{(\zeta)}_k +

@@

By the central limit theorem, as $l_{\zeta} \rightarrow
\infty$ and $l_{\xi} \rightarrow \infty$

@@

  \frac{\phi_{\lambda}(v) - \rho}{\varsigma} \rightsquigarrow

@@

l_{\xi}, p_{10} \Bigr)$. We also set $Y = Y_{\zeta} + Y_{\xi} +
Y_{\omega}$. By the central limit theorem, we have

@@

 \frac{\phi_{\lambda}(v) - \rho}{\varsigma} \rightsquigarrow
 \frac{Y - \rho}{\varsigma}

@@

Eq.~\eqref{eq:21} states that the locality statistics
$\phi_\lambda(v)$ for our
attributed random graphs model at time $t = t^{*}$ can be approximated by
the locality statistics $Y(v)$ for an unattributed kidney and egg
model. Let $G$ be an instance of $\kappa(n,m,p_{11},
p_{10}, p_{00})$, an unattributed kidney-egg graph with the

@@

being $p_{11}$, $p_{10}$, and $p_{00}$, respectively. $D(v) = M(v) + W(v)$ is then the degree

@@

    &\leq P_1 + P_2

@@

We now consider $P_1$. We note that $P_1 \leq R_1 + R_2$
  R_1 &= \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr) \\  
  R_2 &= \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
  d_{n,m}, h(v) \geq a_{n,m} - \vartheta_n \Bigr)
Let us define $g(v) = h(v) - C_{00}p_{00} \tbinom{D(v)}{2}$.
$R_1$ is then bounded as follows
    \label{eq:36}
    R_1 &\leq \mathbb{P}\Bigl( \bigcup_{v \in [m]} h(v) \geq
    a_{n,m} - \vartheta_{n} \Bigr) \\
    % &\leq \mathbb{P}\Bigl( \bigcup_{v \in [n_1]}  C_{00} p_{00}
    % \tbinom{D(v)}{2} \geq a_{n,m} - \vartheta_{n} - g(v) \Bigr) \\
    &\leq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
      \sqrt{\tfrac{2 (a_{n,m} - \vartheta_n -
        g(v))}{C_{00} p_{00}}} \Bigr)
We first consider the term $a_{n,m} - g(v)$. We have
  a_{n,m} - g(v) &= C_{00} p_{00} \tbinom{N_\kappa}{2} \\ &+ (C_{11}p_{11} -
  C_{00} p_{00})(\tbinom{\mu_E}{2} - \tbinom{M(v)}{2})
  \\ &+ (C_{10} p_{10} - C_{00} p_{00})(\mu_E\mu_F - M(v)W(v))
Let $\mathfrak{E}$ and $\mathfrak{F}$ be sets of vertices defined by
\mathfrak{E} &=
\{v \colon |M(v) - \mu_E| \leq \sigma_E \log{m}\} \\ \mathfrak{F} &=
\{v \colon |W(v) - \mu_F| \leq \sigma_F \log{(n-m)}\}.
Then we have, for $v \in \mathfrak{E} \cap \mathfrak{F}$
  \label{eq:34}
  a_{n,m} - g(v) =  C_{00} p_{00} \tbinom{N_\kappa}{2} &+
  \Theta(m^{3/2} \log{m}) \\ &+ 
  \Theta(m \sqrt{n - m}) \\
When $m = \Omega(\sqrt{n \log n})$, Eq.~\eqref{eq:34} gives
  \label{eq:35}
  a_{n,m} - g(v) = N_{\kappa}^{2}\Bigl(\tfrac{C_{00}p_{00}}{2} + O(n^{-1/2 - a}
  \log{n})\Bigr)
for some $a > 0$. The set $\{v \in [m]\}$ can now be partitition into
$\{v \in [m] \cap \mathfrak{E} \cap\mathfrak{F}\}$ and $\{v \in [m]
\setminus (\mathfrak{E} \cap \mathfrak{F})\}$. We can show that
$\mathbb{P}\{v \in [m] \setminus (\mathfrak{E} \cap \mathfrak{F})\} =
o(n^{-1})$ by using a concentration inequality, e.g., Hoeffding's
bound. We thus have
  \label{eq:37}
    R_1 &\leq \mathbb{P}\biggl( \bigcup_{\substack{v \in [m] \\ v
        \in \mathfrak{E} \cap \mathfrak{F}}} D(v) \geq
    N_{\kappa} \sqrt{1 + O(\tfrac{\log{n}}{n^{1/2+a}})} \Bigr) + o(n^{-1}) \\
    & = \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq N_\kappa +
    O(n^{1/2 - a} \log{n})\Bigr) + o(n^{-1}) \\
    &= \mathbb{P}\Bigl(\Delta \geq \mu_{E+F} +
    \sigma_{E+F}(z_m + O(\tfrac{\log{n}}{n^{a}}))\Bigr) + o(n^{-1}) \\ 
    & \rightarrow \mathbb{P}(\Delta \geq N_{\kappa})
The same argument can be applied to $R_2$ to show that
  \label{eq:38}
  R_2 \leq \mathbb{P}\Bigl(\bigcup_{v \in [n] \setminus [m]} D(v) \geq
  N_{\kappa}(1 + o(1))\Bigr) = o(1)
Eq.~\eqref{eq:27} is therefore established.
\begin{proof}[Eq.~\eqref{eq:28}]
  We start by noting that
      \mathbb{P}(\Upsilon(G) \geq a_{n,m}) &=
      \mathbb{P}\Bigl(\bigcup_{v \in [n]}Y(v) \geq
      a_{n,m}\Bigr) \\
      & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]}Y(v) \geq
      a_{n,m}, D(v) \geq N_\kappa \Bigr) \\
      & \geq \mathbb{P}\Bigl(\bigcup_{v \in [m]} D(v) \geq
      N_\kappa\Bigr) \\ &- \mathbb{P}\Bigl( \bigcup_{v
        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa\Bigr)
  We first show $\mathbb{P}( \cup_{v
        \in [m]} Y(v) < a_{n,m}, D(v) \geq N_\kappa) \rightarrow 0$ as
      $n \rightarrow \infty$. Let $v \in [m]$ be arbitrary. It is then
      sufficient to show that $m\mathbb{P}(Y(v) < a_{n,m}, D(v) \geq
      N_{\kappa}) = o(1)$. 

\end{proof}
\bibliography{ssp2011}
\end{document}
